A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-06-23 papers/earths-future/submission.tex
Updates from Overleaf

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2021-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at TBD. % TODO: create Zenodo release!

>>>>

All code, including source code, is available under the GNU Public License (version 3) at \url{https://github.com/jdossgollin/2022-elevation-robustness}.
This code is written in the open source Julia programming language and detailed instructions for reproducing our results are provided.
A permanent, citeable archive of the precise version of the codes used in this study is also available on Zenodo at TBD. % TODO: create Zenodo release!
